### 2023-11-27 thesis/chapters/02-analysis-A-CdM.tex
Incremental learning in thesis

\subsection{Maintenance strategies}
There are three different approaches to maintenance across the industry: \textbf{reactive, preventive, and predictive}~\cite{scheffer_practical_2004}. In general, the more sophisticated methods are beneficial in a high-stakes environment. The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times. In certain situations, it suffices to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize assets' usage~\cite{cinar_machine_2020}.
\bigbreak

\textbf{Reactive maintenance} allows machinery to run until a complete failure. This is the most inappropriate way to maintain the production line, but it is straightforward enough. It requires a large stock of replacement parts on-site and breakage inflicts a `crisis management mode' upon the plant \cite{scheffer_practical_2004}. On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.
\bigbreak

\textbf{Preventive maintenance} is performed before any issue is detected. Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (MTTF - Mean Time To Failure). The schedule is crucial but can result in components being replaced in good condition creating waste. The parts can occasionally stay in operation too long, and the machine breaks as a result. Conservative planning is usually the norm to keep the machine always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
\bigbreak

@@

A measurable decrease in effectivity allows us to order necessary parts in advance and organize repairs of several machines at a convenient time. The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
\bigbreak

@@

The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the `run-to-failure' histories, and usage parameters~\cite{okoh_overview_2014}. Predictive condition monitoring aims to extend lifespan to the maximum by predicting expected RUL.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{assets/bath-tub-curve.png}
	\caption{Bath tub curve~\cite{mohanty_machinery_2015}}
	\label{fig:bath-tub-curve}
\end{figure}

A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded but also in the early stages soon after assembly. Manufacturing or material defects, inadequate installation, or improper start-up procedures, are all suspected causes. During the stable middle phase, malfunction can occur after the machine's excessive overload. The time plot to failure rate is known as the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}).

@@

\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in termos of the vocabulary in ISO 20186. According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or interval. Both designs can be permanently mounted. In continuous collection it is recommended to have `multiplexing rate sufficiently rapid so there is no significant data or trends lost'~\cite{noauthor_iso_2002}. When channels are scanned successively with gaps between data points the system is known as `scanning'.

@@

Broadband measurement requires `frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest'~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s. Bearings and gears diagnosis may push the upper-frequency limit even higher. The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$~(Fig.~\ref{fig:tranducer-response}).

Equipment's `health' can be mischaracterized when there are significant differences in the machine's normal operating conditions. Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation. According to the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}) reference signatures should be obtained after the initial part wear-in period. The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.

>>>>

\subsection{Maintenance strategies}
There are three different approaches to maintenance across the industry: \textbf{reactive, preventive, and predictive}~\cite{scheffer_practical_2004}. In general, the more sophisticated methods are beneficial in a high-stakes environment. The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times. In certain situations, it suffices to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize usage of assets~\cite{cinar_machine_2020}.

\textbf{Reactive maintenance} allows machinery to run until a complete failure. This is the most inappropriate way to maintain the production line, but it is straightforward enough. It requires a large stock of replacement parts on-site and breakage inflicts a ``crisis management mode'' upon the plant \cite{scheffer_practical_2004}. On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.

\textbf{Preventive maintenance} is performed before any issue is detected. Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (MTTF - Mean Time To Failure). The schedule is crucial but can result in components being replaced in good condition creating waste. The parts can occasionally stay in operation too long, and the machine breaks as a result. Conservative planning is usually the norm to keep the machine always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.

@@

A measurable decrease in effectivity allows us to order necessary parts in advance and organize repairs of several machines at a convenient time. The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.

@@

The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the ``run-to-failure'' histories, and usage parameters~\cite{okoh_overview_2014}. Predictive condition monitoring aims to extend lifespan to the maximum by predicting expected RUL.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\textwidth]{assets/bath-tub-curve.png}
	\caption{Bathtub curve~\cite{mohanty_machinery_2015}}
	\label{fig:bathtub-curve}
\end{figure}

A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded but also in the early stages soon after assembly. Manufacturing or material defects, inadequate installation, or improper start-up procedures, are all suspected causes. During the stable middle phase, malfunction can occur after the machine's excessive overload. The time plot to failure rate is known as the bathtub curve~(Fig.~\ref{fig:bathtub-curve}).

@@

\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in termos of the vocabulary in ISO 20186. According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or interval. Both designs can be permanently mounted. In continuous collection it is recommended to have ``multiplexing rate sufficiently rapid so there is no significant data or trends lost''~\cite{noauthor_iso_2002}. When channels are scanned successively with gaps between data points the system is known as ``scanning''.

@@

Broadband measurement requires ``frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest''~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s. Bearings and gears diagnosis may push the upper-frequency limit even higher. The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$~(Fig.~\ref{fig:tranducer-response}).

Equipment's ``health'' can be mischaracterized when there are significant differences in the machine's normal operating conditions. Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation. According to the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}) reference signatures should be obtained after the initial part wear-in period. The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.
